Education Analysis of the United States

### 2023-03-16 outputs/paper/paper.qmd
Paper Adjustments

---
title: "Generational Difference in Highest Obtained Education Level"
author: 
  - Jueun Kang
  - Tayedza Chikumbirike
thanks: "Code and data are available at: https://github.com/tayedzac/GSS_education."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "This paper discusses the generational difference in highest education level by looking at the highest level of education obtained by respondents in comparison to their mothers and fathers. We find that the majority of respondents have more than 4 years of college as their highest education level, while both their mothers and fathers have high school as their highest education level, as reported in 2021. We also find that where mothers and fathers have 4 years of college as their highest education level, so do the respondents. These findings matter as we are able to further explore the generational difference in the required education level to work."
format: pdf
number-sections: true
bibliography: references.bib
---
# Introduction
Education is widely recognized to be the foundation of one’s success, playing a crucial role in opening new opportunities and shaping our society [@education]. When looking at students in particular, education holds many benefits. Through illuminating one’s mind and ways of thinking, education provides a pathway for students to plan for employment or pursue higher education, it grants one to have a good status within society, and self-confidence, contributing to an arguably, more “successful” life.

@@

clean_data_mom |> 
  ggplot(aes(x = education)) +
  geom_bar(fill = "violet") +
  theme_minimal() +
  labs(x = "Highest Education Level",
       y = "Number of Participants",
       title = "Education Level of Respondants' Mother.")
```
\newpage
@fig-2 presents a bar graph showing the highest degree of education completed by respondents’ mothers, by 2021. We see that the majority of respondents’ mothers earned a high school degree as their highest degree of education. We also see that the number of mothers who obtain an education level beyond a high school degree becomes progressively lower as just under 500 mothers have some college education and less than 250 mothers with more than 4 years of college.

>>>>

---
title: "Education Analysis of the United States"
subtitle: "Exploring the Generational Difference in Highest Obtained Education Level in 2021"
author: 
  - Jueun Kang
  - Tayedza Chikumbirike
thanks: "Code and data are available at: https://github.com/tayedzac/GSS_education."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "This paper discusses the generational difference in highest education level by looking at the highest level of education obtained by respondents in comparison to their mothers and fathers. We find that the majority of respondents have more than 4 years of college as their highest education level, while both their mothers and fathers have high school as their highest education level, as reported in 2021. We also find that where mothers and fathers have 4 years of college as their highest education level, so do the respondents. These findings matter as we are able to further explore the generational difference in the required education level to work."
format: pdf
number-sections: true
bibliography: references.bib
---
# Introduction
Education is widely recognized to be the foundation of one’s success, playing a crucial role in opening new opportunities and shaping our society [@education]. When looking at students in particular, education holds many benefits. Through illuminating one’s mind and ways of thinking, education provides a pathway for students to plan for employment or pursue higher education, it grants one to have a good status within society, and self-confidence, contributing to an arguably, more “successful” life.

@@

clean_data_mom |> 
  ggplot(aes(x = education)) +
  geom_bar(fill = "violet") +
  theme_minimal() +
  labs(x = "Highest Education Level",
       y = "Number of Participants",
       title = "Education Level of Respondants' Mother.")
```
@fig-2 presents a bar graph showing the highest degree of education completed by respondents’ mothers, by 2021. We see that the majority of respondents’ mothers earned a high school degree as their highest degree of education. We also see that the number of mothers who obtain an education level beyond a high school degree becomes progressively lower as just under 500 mothers have some college education and less than 250 mothers with more than 4 years of college.
